Data Preparation

### 2019-01-09 Data Preparation.Rmd
Including libraries and importing manuals

---
title: "Data Preparation"
author: "DARS"
date: "1/9/2019"
output: pdf_document
---

# Import Data

>>>>

---
title: "Data Preparation"
author: "DARS"
date: "1/9/2019"
output: pdf_document
---
#Libraries:
```{r setup, include=FALSE}

library(tidyverse)
library(tidytext)

library(tm          ) # text mining
library(topicmodels)  #topic modeling

library(pdftools)
library(ggplot2)

```

# Import Data
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
